Formalization of Forcing in Isabelle/ZF \thanks{Supported by Secyt-UNC project 33620180100465CB and Conicet.}

### 2019-12-19 IJCAR2020/intro.tex
enumeración de (algunos) avances por sobre Separation

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "forcing_in_isabelle_zf"
%%% ispell-local-dictionary: "american"
%%% End:

>>>>

\subsection{Related work}

Han \& van Doorn \cite{han_et_al:LIPIcs:2019:11074}.

Updates over the (unpublished) technical report \cite{2019arXiv190103313G}.

\begin{enumerate}
\item The development is now independent of $\AC$: We modularized the
  Rasiowa-Sikorski lemma in such a way that a version for countable
  posets does not require choice, while we have the full result in an
  independent file.
  %
\item We lifted the restriction on arities on the axiom schemes of
  Separation and Replacement, streamlining various proofs as an
  immediate benefit and avoiding the need for tupling. 
  %
\item We fulfilled the promised formal abstract for the Forcing
  Theorems almost to the letter, with some slight modification
  regarding arities of formulas.
  %
\item We implemented an automatic ML machinery of (bounded) renaming
  of formulas.
\item We finished the inteface between our development and
  \isatt{ZF-Constructible} which enables us to do well-founded
  recursion inside transitive models of an appropriate finite fragment
  of $\ZF$. As a consequence, we have an unconditional proof of
  the Axiom of Infinity and a long debt: the fact that the generic
  filter $G$ belongs to the extension $M[G]$ and $M\sbq M[G]$.
\end{enumerate}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "forcing_in_isabelle_zf"
%%% ispell-local-dictionary: "american"
%%% End:
